Paper 2 !DRAFT! Do not circulate!

### 2014-09-21 Articles/Article_EcolEcon_2014/Paper2.Rnw
1978=1 --> 1970=1

<<Historical_Data_1, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=7, fig.cap="Historical data.">>=
mdata <- melt(historicalData, 
              measure.vars = c("iGDP", "iK", "iL", "iXp", "iXf", "iU"), 
              variable.name = "variable",
              value.name = "value")
historicalPlot(mdata, 
               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
               facet_formula = Country ~ Source, 
               line_types = c(1,5,2,6,4,3)) + 
  xlab("") + 
  ylab("Indexed (1960=1 or 1978=1)")
@

@@

<<Historical_Data_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Historical data.">>=
historicalPlot(mdata, 
               mapping=aes(x=Year, y=value, group=Source, linetype=Source), 
               facet_formula = Country ~ variable, 
               line_types = c(1,5,3)) + 
  xlab("") + 
  ylab("Indexed (1960=1 or 1978=1)")
@

@@

historicalPlot(mdata2, 
               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
               facet_formula = Country ~ Source, 
               line_types = c(1,5,2,6,4)) + 
  xlab("") + 
  ylab("Indexed Econometric Ratios (1960=1 or 1978=1)")
@

@@

<<Preeconometric_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Pre-econometric data.">>=
historicalPlot(mdata2, 
               mapping=aes(x=Year, y=value, group=Source, linetype=Source), 
               facet_formula = Country ~ variable, 
               line_types = c(1,3,5)) + 
  xlab("") + 
  ylab("Indexed Econometric Ratios (1960=1 or 1978=1)")
@

>>>>

<<Historical_Data_1, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=7, fig.cap="Historical data.">>=
mdata <- melt(historicalData, 
              measure.vars = c("iGDP", "iK", "iL", "iXp", "iXf", "iU"), 
              variable.name = "variable",
              value.name = "value")
historicalPlot(mdata, 
               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
               facet_formula = Country ~ Source, 
               line_types = c(1,5,2,6,4,3)) + 
  xlab("") + 
  ylab("Indexed (1960=1 or 1970=1)")
@

@@

<<Historical_Data_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Historical data.">>=
historicalPlot(mdata, 
               mapping=aes(x=Year, y=value, group=Source, linetype=Source), 
               facet_formula = Country ~ variable, 
               line_types = c(1,5,3)) + 
  xlab("") + 
  ylab("Indexed (1960=1 or 1970=1)")
@

@@

historicalPlot(mdata2, 
               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
               facet_formula = Country ~ Source, 
               line_types = c(1,5,2,6,4)) + 
  xlab("") + 
  ylab("Indexed Econometric Ratios (1960=1 or 1970=1)")
@

@@

<<Preeconometric_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Pre-econometric data.">>=
historicalPlot(mdata2, 
               mapping=aes(x=Year, y=value, group=Source, linetype=Source), 
               facet_formula = Country ~ variable, 
               line_types = c(1,3,5)) + 
  xlab("") + 
  ylab("Indexed Econometric Ratios (1960=1 or 1970=1)")
@
